---
title: "yutingq2_final_CDAP"
author: "Yuting Qiu"
date: "12/12/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(lme4)
library(lmerTest)
library(lsmeans)
library(reshape2)
library(dplyr)
library(ggplot2)
library(glmnet)
library(caret)
library(MASS)
library(tidyverse)


read.table("examFile.csv", sep=",",header= TRUE,na.strings = "NA")->df
# remove the genotype variable
df_clean <- df[,1:7]

# replace east with north, replace west with south
df_clean$Reg <- replace(as.character(df_clean$Reg), df_clean$Reg == "east", "north")
df_clean$Reg <- replace(as.character(df_clean$Reg), df_clean$Reg == "west", "south")
```


# Obj 1.	Evaluate location effects: 
## a.	What fraction of the variation observed in yield is attributable to Location specific effects? 
```{r}
model1 <- lm(Estimate~Loc, data=df_clean)
anova(model1) #location effect is significant
summary(model1)$adj.r.squared #0.7925499
``` 
79.25% of the variation observed in the yield is attributable to location specific effect


## b.	Which location seems to be the highest yield location?
```{r}
summary(model1)
#Coefficients:
#                  Estimate Std. Error t value Pr(>|t|)    
#(Intercept)        76.7404     0.6190  123.97   <2e-16 ***
#LocElkville_2019   24.4245     0.8755   27.90   <2e-16 ***
#LocHampshire_2019  34.0239     0.9080   37.47   <2e-16 ***
#LocNeoga_2018      14.7687     0.8755   16.87   <2e-16 ***
#LocPerry_2019      14.4606     0.9080   15.93   <2e-16 ***
#LocUrbana_2018     19.4130     0.9504   20.43   <2e-16 ***
```
Hampshire_2019 is the highest yield location.


# Obj 2.	Evaluate company/ brand effects: 
## a.	Which company's varieties seem to perform the best across all regions? 
## b.	Which company's varieties seem to perform the worst across all regions?
```{r}
model2 <- lm(Estimate~Company, df_clean)
anova(model2)
summary(model2)
```
[Best] Moiner_Seed variaty perform the best across all regions, but the s.e. for this company is large and thus this company doesn't have a significant effect on the yield, thus DeRaedt_Seed can be a good choice
[Worst] Go_Wheat variaty perform the worst across all regions


## c.	Which company's varieties seem to perform the best for each location? 
## d.	Which company's varieties seem to perform the worst for each location?
```{r}
as.data.frame(aggregate(x=df_clean$Estimate,
          by=list(df_clean$Loc,df_clean$Company),
          FUN=mean)) -> ag2
```
[perform the best]
* Hampshire_2019	Pioneer
* Elkville_2019	KWS_Cereals
* Urbana_2018	Pioneer
* Perry_2019	Pioneer
* Neoga_2018	Croplan
* Belleville_2019	Pioneer

[perfrom the worst]
* Belleville_2019	ProHarvest
* Neoga_2018	Miller_Bros_Farm_and_Fert.
* Elkville_2019	ProHarvest
* Perry_2019	ProHarvest
* Urbana_2018	Kratz_Farms
* Hampshire_2019	Kratz_Farms


# Obj 3.	Evaluate variety effects:
## a.	Which varieties seem to perform the best across all regions? 
## b.	Which varieties seem to perform the worst across all regions?
```{r}
aggregate(x=df_clean$Estimate,
          by=list(df_clean$Variety),
          FUN=mean) %>% 
  as.data.frame() -> ag3.1

```
Variety DeRaedt_24 performs the best across all regions
Variety EXP18-1 performs the worst across all regions


## c.	Which varieties seem to perform the best for each location? 
## d.	Which varieties seem to perform the worst for each location?

```{r}
aggregate(x=df_clean$Estimate,
          by=list(df_clean$Variety, df_clean$Loc),
          FUN=mean) %>% 
  as.data.frame() -> ag3.2
```
[varieties perform the best for each location]
* WX18C	at Urbana_2018	with 108.3 bu/acre
* 495	at Perry_2019 with	103.7 bu/acre
* H7W18 at	Neoga_2018 with	105.2 bu/acre 
* KWS19X03 at	Hampshire_2019	with 125.6 bu/acre
* KWS19X09 at	Elkville_2019	with 113.5 bu/acre
* KWS19X07 at	Belleville_2019	with 93.4 bu/acre

[varieties perform the worst for each location]
* 851 and Lewis_851	at Urbana_2018 with	87.6 bu/acre
* KF_15334 at	Perry_2019 with	79.4 bu/acre
* FS_604 at	Neoga_2018 with	79.4 bu/acre
*	KF_15334	at Hampshire_2019	with 97.0 bu/acre
*	286	at Elkville_2019	with 83.3 bu/acre
*	317	at Belleville_2019 with	60.3 bu/acre



# Obj 4.	Evaluate regional effects( north/south) :
## a.	How much variation in yield does region explain alone? 
## b.	How about together with Company? 
```{r}
model.4.1 <- lm(Estimate ~ Reg, data = df_clean)
summary(model.4.1)$adj.r.squared # 0.1623734
anova(model.4.1)

model.4.2 <- lm(Estimate ~ Reg + Company, data = df_clean)
anova(model.4.2)
summary(model.4.2)$adj.r.squared # 0.1910692
```
* Region alone explain 16.24% of variation in yield.
* Together with comapany, 19.1% of variation in yield was explained. 


## c.	Which company's varieties seem to perform the best within each region? 
## d.	Which company's varieties seem to perform the worst within each region?
```{r}
library(dplyr)
as.data.frame(aggregate(x=df_clean$Estimate,
          by=list(df_clean$Reg,df$Company),
          FUN=mean)) -> ag4.1
```
[company that perform the best within each region]
* company DeRaedt_Seed at south region
* company Moiner_Seed at north region

[company that perform the worst within each region]
* comapny	ProHarvest at south region
* Miller_Bros_Farm_and_Fert at north region


## e.	Which variety is best suited to each region?
```{r}
as.data.frame(aggregate(x=df_clean$Estimate,
          by=list(df_clean$Reg,df$Variety),
          FUN=mean)) -> ag4.2
```
* variety	KWS19X03 best suited to north region 
* variety	CP9606 best suited to south region


## f.	Which variety is best suited to each location?
```{r}
as.data.frame(aggregate(x=df_clean$Estimate,
          by=list(df_clean$Loc,df$Variety),
          FUN=mean)) -> ag4.3
```
* Belleville_2019: variety KWS19X07  
* Elkville_2019: variety	KWS19X09
* Hampshire_2019: variety	KWS19X03
* Neoga_2018: variety	H7W18	
* Perry_2019: variety	495
* Urbana_2018: variety WX18C	


# Obj 5.	Does the seed treatments have a significant effect on the yield? 
## a.	Which treatment seems to have the largest positive effect? Is it significant?
```{r}
model5.1 <- lm(Estimate ~ SeedTreatment, df_clean)
anova(model5.1)
summary(model5.1)
```
Seed treatment itself have a signficant positive effect. Treatment C is the largest with signigicant effect.


## b.	What fraction of the variation observed in yield is attributable to seed treatments?
```{r}
summary(model5.1)$adj.r.squared
```
0.85% of the variarion observed in yield is attributable to seed treatment.


## c.	Is seed treatment recommended?
```{r}
model5.2 <- lm(Estimate ~ Loc + SeedTreatment, df_clean)
anova(model5.2) 
summary(model5.2)
```
seed treatment is not signifiant any more when look together with other factors, thus there is no need to apply seed treatment



# Obj 6. Give your best prediction of maximum yield under these best case scenario conditions. 
## a.	Which location variety combinations should be used to get the maximum yield? 
```{r}
# split the data
df_south <- df_clean[df_clean$Reg=="south",]
df_north <- df_clean[df_clean$Reg=="north",]

# find the best model 
fit_int <- lm(Estimate ~ 1, data=df_clean)
fit_full <- lm(Estimate ~ Company + Loc + Reg + SeedTreatment + Variety, data=df_clean)
step(fit_int,scope = list(upper = formula(fit_full), lower = formula(fit_int)), direction = 'both')

# fit the best model for each region seperately
## south
model.6.south <- lm(Estimate ~ Loc + Variety, data=df_south)
summary(model.6.south)

best.v.l_1 <- data.frame(
   Loc = "Elkville_2019",Variety="CP9606"
)
best.v.l_2<- data.frame(
   Loc = "Elkville_2019",Variety="SRW_9606"
)
predict(model.6.south, best.v.l_1)
# 112.0956 
predict(model.6.south, best.v.l_2)
# 112.0956 

## north
model.6.north <- lm(Estimate ~ Loc + Variety, data=df_north)
summary(model.6.north)
# Hampshire_2019	VarietyKWS19X03 
best.v.l_3 <- data.frame(
   Loc = "Hampshire_2019",Variety="KWS19X03"
)
predict(model.6.north, best.v.l_3)
# 125.6498 
```
At location Hampshire_2019 use variety "KWS19X03" can get the best yield prediction

## b.	Is paying a premium for Seed Treatment justified? 
```{r}
model.6.south <- lm(Estimate ~ Loc + Variety, data=df_south)
model.6.south_sd <- lm(Estimate ~ Loc + Variety + SeedTreatment, data=df_south)
anova(model.6.south, model.6.south_sd)

model.6.north <- lm(Estimate ~ Loc + Variety, data=df_north)
model.6.north_sd <- lm(Estimate ~ Loc + Variety + SeedTreatment, data=df_north)
anova(model.6.north, model.6.north_sd)
```
No differnce in terms of the efficiency of the model for both south and north region, no need to use seed treatment

## c.	Report the best prediction of maximum yield under these best case scenario conditions for each variety for each region and location.
```{r}
# south region (Perry_2019; Belleville_2019; Elkville_2019)

# Elkville_2019
best.v.l_1 <- data.frame(
   Loc = "Elkville_2019",Variety="CP9606"
)
best.v.l_2<- data.frame(
   Loc = "Elkville_2019",Variety="KWS19X09"
)
predict(model.6.south, best.v.l_1)# 112.0956  # selected by summary
predict(model.6.south, best.v.l_2)# 106.3485 selected by mean
 

# Perry_2019
best.v.l_4 <- data.frame(
   Loc = "Perry_2019",Variety="CP9606"
)
best.v.l_5<- data.frame(
   Loc = "Perry_2019",Variety="25R61"
)
best.v.l_5.1<- data.frame(
   Loc = "Perry_2019",Variety="495"
)
predict(model.6.south, best.v.l_4) # 102.0142(not show up)  # selected by summary
predict(model.6.south, best.v.l_5) # 98.59835 the second best variety and also tested in this location 
predict(model.6.south, best.v.l_5.1) # 96.63376 select by mean

# Belleville_2019
best.v.l_6 <- data.frame(
   Loc = "Belleville_2019",Variety="CP9606"
)
best.v.l_7<- data.frame(
   Loc = "Belleville_2019",Variety="KWS19X07"
)
predict(model.6.south, best.v.l_6) # 87.67107  # selected by summary
predict(model.6.south, best.v.l_7) # 82.52397  # selected by mean  

# north region (Hampshire_2019; Urbana_2018; Neoga_2018)
# Hampshire_2019
best.v.l_8<- data.frame(
   Loc = "Hampshire_2019",Variety="KWS19X03"
)
predict(model.6.north, best.v.l_8)# 125.6498 selected by summary and mean


# Urbana_2018
best.v.l_9 <- data.frame(
   Loc = "Urbana_2018",Variety="WX18C"
)
best.v.l_10<- data.frame(
   Loc = "Urbana_2018",Variety="KWS19X03"
)
best.v.l_10.1<- data.frame(
   Loc = "Urbana_2018",Variety="WX18C"
)
predict(model.6.north, best.v.l_9)# 101.3564 selected by mean
predict(model.6.north, best.v.l_10)# 110.6896 selected by summary_not show up


# Neoga_2018
best.v.l_11 <- data.frame(
   Loc = "Neoga_2018",Variety="H7W18"
)
best.v.l_12<- data.frame(
   Loc = "Neoga_2018",Variety="KWS19X03"
)
best.v.l_12.1<- data.frame(
   Loc = "Neoga_2018",Variety="3404"
)
predict(model.6.north, best.v.l_11) #  105.2071 selected by mean
predict(model.6.north, best.v.l_12) # 105.0126 selected by summary_not show up
predict(model.6.north, best.v.l_12.1) # 95.73333 as second high by summary

```

* In the north region, at location Hampshire_2019, use variety "KWS19X03" can get the best yield, being 125.65 bu/acre. 
* In the south region, at location Elkville_2019, use either CP9606 or SRW_9606 can get the maximum yield, being 112.1 bu/acre. 




