---
title: "Neoga Exploratory Analysis"
author: "Taylor"
date: "12/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages needed
```{r}
library(ggplot2)
```
## Read in data

```{r cars}

neoga<-read.csv("Neoga_2018.csv",header=TRUE)
neoga$Location<-"Neoga"
str(neoga)
```

## Graphs needed

# Box Plots and Density Plots Across Locations




##Box Plots and Density Plots by Location
```{r}
# Box plot for Yield values for Neoga
ggplot(neoga, aes(x= Location, y=Yield)) + 
    geom_boxplot(fill="lightblue") + 
    labs(x="Location",y="Yield Estimate (bu/ac)")
# Density plot for Yield values for Hampshire
ggplot(neoga, aes(x=Yield)) +
    geom_density(adjust=1.5, fill = "lightblue") +
  xlab("Yield estimate (bu/ac)")
```
##Box Plots and Density Plots by Company
```{r}
# Box plot for Yield values for Neoga
neoga$Company = with(neoga, reorder(Company, Yield, median))
p<-ggplot(neoga, aes(x= Company, y=Yield)) + 
    geom_boxplot(fill="lightblue") + 
    labs(x="Company",y="Yield Estimate (bu/ac)")
p + theme(axis.text.x = element_text(angle = 45))
# Density plot for Yield values for Hampshire
ggplot(neoga, aes(x=Yield, group=Company)) +
    facet_wrap(~Company)+
    geom_density(adjust=1.5, fill = "lightblue") +
  xlab("Yield estimate (bu/ac)")
```



## Pairs Plots for within location variation

```{r}
pairs(neoga[,4:9])
```
# Initial linear regression fit evaluation: Diagnostic plots
```{r}
fit.company<-lm(Yield~Company, data=neoga)
summary(fit.company)
plot(fit.company) #plot diagnostic plots
```
# Initial linear regression fit evaluation: curve fitting plot (2D scatter plot + density plot)
```{r}
ggpairs(neoga[, c(4:9)])
```

